Energy and the CES production function

### 2015-08-21 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Eliminated sci notation on x axis.

<<setup, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE>>=
library(EconData)
library(EconModels)
library(dplyr)
library(reshape2)
library(ggplot2)
library(mosaic)
library(xtable)
library(knitr)
library(texreg)
library(tidyr)

@@

<<sigma_graph_2, fig.pos="H", fig.align='center', fig.width=8.5, fig.height=5, out.width="0.9\\textwidth", fig.cap="Elasticities of substitution~($\\sigma$).">>=
p <- 
ggplot(
  AllCoeffs %>% 
    gather(type, value, matches("sigma")) %>% 
    filter(!is.na(value)) %>% 
    filter(! type %in% c("sigma", "sigma_1")) %>%
    mutate(Model = interaction(nest, CSP, sep = " ", drop=TRUE),
           Inputs = flavor
           )
  ) + 
  geom_point(aes(x=value, y=type, 
                 shape = Model, fill=Model, size=Model,
                 color=Inputs
                 )
                 #position = position_jitter(height=0.2, width=0)
             ) + 
  facet_grid( type ~ Country, scales = "free_y" ) + 
  scale_x_log10(limits = c(0.001,2000)) +
  geom_vline(xintercept = 1, color="gray50", size=0.2) +
  xy_theme() +
  theme(legend.position="top")

>>>>

<<setup, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE>>=
library(EconData)
library(EconModels)
library(dplyr)
library(reshape2)
library(ggplot2)
library(mosaic)
library(xtable)
library(knitr)
library(texreg)
library(tidyr)
library(scales)

@@

<<sigma_graph_2, fig.pos="H", fig.align='center', fig.width=8.5, fig.height=5, out.width="0.9\\textwidth", fig.cap="Elasticities of substitution~($\\sigma$).">>=
p <- 
ggplot(
  AllCoeffs %>% 
    gather(type, value, matches("sigma")) %>% 
    filter(!is.na(value)) %>% 
    filter(! type %in% c("sigma", "sigma_1")) %>%
    mutate(Model = interaction(nest, CSP, sep = " ", drop=TRUE),
           Inputs = flavor
           )
  ) + 
  geom_point(aes(x=value, y=type, 
                 shape = Model, fill=Model, size=Model,
                 color=Inputs
                 )
                 #position = position_jitter(height=0.2, width=0)
             ) + 
  facet_grid( type ~ Country, scales = "free_y" ) + 
  scale_x_log10(limits = c(0.001,2000), labels=comma) +
  xlab("") +
  geom_vline(xintercept = 1, color="gray50", size=0.2) +
  ylab("") +
  xy_theme() +
  theme(
    legend.position="top",
    strip.text.y = element_blank())
